|

### 2019-07-26 appendix/appendix-institutional-design-climate-policy.Rmd
revised version

---
title: |
       | Supplementary Materials for "Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries"
author: 
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "David Skarbek[^skarbek]"
date: July 22, 2019
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
load('freire-mignozzetti-skarbek.RData')

plot_mm <- function(
  x,
  group = attr(x, "by"),
  feature_headers = TRUE,
  header_fmt = "%s",
  size = 2,
  xlab = "Marginal Mean",
  ylab = "",
  legend_title = if (is.null(group)) "Feature" else group,
  legend_pos = "bottom",
  xlim = NULL,
  vline = 0,
  vline_color = "gray",
  theme = ggplot2::theme_bw(),
  ...
) {

  # function used in cj and ammplot to produce "fancy" feature labels
  clean_feature_labels <- function(data, RHS, feature_labels) {
    if (inherits(data, "cj_df") | inherits(data, "data.frame")) {
      fancy_labels <- stats::setNames(lapply(data[RHS], attr, "label"), RHS)
    } else if (inherits(data, "survey.design")) {
      fancy_labels <- stats::setNames(lapply(data[["variables"]][RHS], attr, "label"), RHS)
    } else {
      stop("'data' is not a 'data.frame' or 'survey.design' object")
    }
    ## check `feature_labels`, if present
    missing_labels <- RHS[!RHS %in% names(feature_labels)]
    feature_labels <- c(feature_labels, stats::setNames(rep(list(NULL), length(missing_labels)), missing_labels))
    ## clean fancy labels (use variable name if variable has no "label" attribute)
    for (i in seq_along(feature_labels)) {
      if (is.null(feature_labels[[i]]) || feature_labels[[i]] == "") {
        if (is.null(fancy_labels[[RHS[i]]])) {
          feature_labels[[i]] <- RHS[i]
        } else {
          feature_labels[[i]] <- fancy_labels[[RHS[i]]]
        }
      }
    }
    return(feature_labels)
  }

  # function to cleanup term labels (due to factor variable blah blah)
  clean_term_names <- function(x, RHS) {
    out <- data.frame(feature = character(length(x)), 
                      level = character(length(x)), 
                      stringsAsFactors = FALSE)
    for (i in seq_along(RHS)) {
      w <- grepl(RHS[i], x)
      out$feature[w] <- RHS[i]
      out$level[w] <- sub(paste0("^`?", RHS[i], "`?"), "", x[w])
    }

    # check whether levels are all unique
    if (any(duplicated(out$level))) {
      warning("Some level labels are duplicated across features. This may cause problems!")
    }

    return(out)
  }

  # function used to produce a data frame of features and levels
  make_term_labels_df <- function(data, feature_names, level_order = c("ascending", "descending")) {
    # setup data
    if (inherits(data, "data.frame")) {
      term_levels_list <- lapply(data[feature_names], levels)
    } else if (inherits(data, "survey.design")) {
      term_levels_list <- lapply(data[["variables"]][feature_names], levels)
    } else {
      stop("'data' is not a 'data.frame' or 'survey.design' object")
    }

    # figure out level order
    level_order <- match.arg(level_order)
    if (level_order == "descending") {
      term_levels_list[] <- lapply(term_levels_list, rev)
    }

    # construct data frame
    term_levels <- rev(unlist(term_levels_list))
    term_labels <- stats::setNames(rep(feature_names, lengths(term_levels_list)), rev(term_levels))
    data.frame(feature = unlist(term_labels), level = unlist(names(term_labels)), stringsAsFactors = FALSE)
  }

  # function used in plot() methods to make pretty feature headers
  make_feature_headers <- function(x, fmt = "(%s)") {
    feature_levels <- rev(split(x$level, x$feature))
    for (i in seq_along(feature_levels)) {
      feature_levels[[i]] <- levels(x$level)[match(feature_levels[[i]], levels(x$level))]
      feature_levels[[i]] <- c(feature_levels[[i]], sprintf(fmt, names(feature_levels)[i]))
    }
    factor(as.character(x$level), levels = unique(unname(unlist(feature_levels))))
  }

  # function used to check whether, if specified, the 'feature_order' argument is valid
  check_feature_order <- function(feature_order, RHS) {
    if (!is.null(feature_order)) {
      if (length(RHS) > length(feature_order)) {
        stop("'feature_order' appears to be missing values")
      } else if (length(RHS) < length(feature_order)) {
        stop("'feature_order' appears to have excess values")
      } else if (any(!names(feature_order) %in% RHS)) {
        stop("'feature_order' appears to contain erroneous values")
      }
    } else {
      feature_order <- RHS
    }
    return(feature_order)
  }

  # optionally, add gaps between features
  if (isTRUE(feature_headers)) {
    x$level <- make_feature_headers(x, fmt = header_fmt)
    to_merge <- data.frame(feature = unique(x$feature), level = sprintf(header_fmt, unique(x$feature)))
    if ("BY" %in% names(x)) {
      to_merge <- do.call("rbind", lapply(unique(x[["BY"]]), function(lev) {
        to_merge[["BY"]] <- lev
        to_merge
      }))
    } else if (!is.null(group)) {
      to_merge <- do.call("rbind", lapply(unique(x[[group]]), function(lev) {
        to_merge[[group]] <- lev
        to_merge
      }))
    }
    x <- merge(x, to_merge, all = TRUE)
  }

  if (is.null(group)) {
    p <- ggplot2::ggplot(data = x, ggplot2::aes_string(x = "estimate", y = "level", colour = "feature"))
  } else {
    p <- ggplot2::ggplot(data = x, ggplot2::aes_string(x = "estimate", y = "level", colour = group, group = group))
  }

  if (is.null(xlim)) {
    xmin <- min(x$lower, na.rm = TRUE)
    xmin <- if (xmin < 0) 1.04*xmin else .96*xmin
    xmax <- max(x$upper, na.rm = TRUE)
    xmax <- if (xmax > 0) 1.04*xmax else .96*xmax
    xlim <- c(xmin, xmax)
  }

  if (!is.null(vline)) {
    p <- p + ggplot2::geom_vline(xintercept = vline, colour = vline_color)
  }

  ggplotColours <- function(n = 6, h = c(0, 360) + 15){
    if ((diff(h) %% 360) < 1) h[2] <- h[2] - 360/n
    hcl(h = (seq(h[1], h[2], length = n)), c = 100, l = 65)
  }
  myColors <- ggplotColours(length(unique(x$feature)))
  myColors <- c(rep(myColors[1], 6), rep(myColors[2], 5),
                rep(myColors[3], 4), rep(myColors[4], 5),
                rep(myColors[5], 6), rep(myColors[6], 6))
  myFaces <- c(rep('plain', 5), "bold",
               rep('plain', 4), "bold",
               rep('plain', 3), "bold",
               rep('plain', 4), "bold",
               rep('plain', 5), "bold",
               rep('plain', 5), "bold")
  mySizes <-  c(rep(10, 5), 11,
               rep(10, 4), 11,
               rep(10, 3), 11,
               rep(10, 4), 11,
               rep(10, 5), 11,
               rep(10, 5), 11)
  myColors <- rep(myColors, ifelse(length(unique(x[,group])), length(unique(x[,group])), 1))

  p <- p + ggplot2::geom_point(position = ggstance::position_dodgev(height = 0.75), 
                               size = size, na.rm = TRUE, color = myColors) +
    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower", xmax = "upper"),  
                            size = 0.7, height = 0, na.rm = TRUE, color = myColors,
                            position = ggstance::position_dodgev(height = 0.75))
  if (is.null(group)) {
    p <- p + ggplot2::scale_colour_discrete(guide = ggplot2::guide_legend(title = legend_title))
  } else {
    p <- p + ggplot2::scale_colour_discrete(breaks = levels(x[[group]]),
                                            labels = levels(x[[group]]),
                                            guide = ggplot2::guide_legend(title = legend_title))
  }
  p <- p + theme_bw() +
    ggplot2::scale_x_continuous(limits = xlim, oob = scales::rescale_none) +
    ggplot2::xlab(xlab) + 
    ggplot2::ylab(ylab) + 
    theme + ggplot2::theme(
      legend.position = legend_pos,
      panel.grid.major = ggplot2::element_blank(),
      panel.grid.minor = ggplot2::element_blank(),
      axis.text.y = element_text(face=myFaces, size = mySizes)
    ) + 
    ggplot2::guides(colour = ggplot2::guide_legend(title = legend_title))
  return(p)
}

@@

# Function
table_mm <- function(mms, capt) {
  dfr <- data.frame(feature = mms[,c(4)], 
             round(mms[,c(5,6,8,9,10)], digits=3))
  names(dfr) <- c('Feature', 'Estimate', 'Std.Error',
                'P-Value', 'Lower', 'Upper')
  return(kable(dfr, "latex", caption = capt, booktabs = T) %>%
    kable_styling(font_size = 10) %>%
    group_rows('Who makes the rules?', 1, 5) %>%
    group_rows('How are conflicts resolved?', 6, 10) %>%
    group_rows('What punishments do they use?', 11, 14) %>%
    group_rows('How are repeated violations punished?', 15, 17) %>%
    group_rows('How are costs distributed?', 18, 21) %>%
    group_rows('How often will the agreement be renegotiated?', 22, 26))
}

tableAMCE <- function(results, capt = 'Main Model') {
  aux <- plotAMCE(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Full Model',
     attribute.names = attrs, tblfy = T)
  aux <- aux %>%
    filter(!is.na(group))%>%
    select(printvar, pe, se, lower, upper)
  indx <- grep('Baseline =', aux$printvar)
  aux$pe <- round(aux$pe, digits = 3)
  aux$se <- round(aux$se, digits = 3)
  aux$lower <- round(aux$lower, digits = 3)
  aux$upper <- round(aux$upper, digits = 3)
  aux$pe[indx] = ''
  aux$se[indx] = ''
  aux$lower[indx] = ''
  aux$upper[indx] = ''
  names(aux) <- c('Feature', 'Estimate', 'Std.Error', 
                  'Lower', 'Upper')
  return(kable(aux, "latex", caption = capt, booktabs = T, align = c('l', rep('c', 4))) %>%
    kable_styling(font_size = 10) %>%
    group_rows('How are conflicts resolved?', 1, 5) %>%
    group_rows('How are costs distributed?', 6, 9) %>%
    group_rows('How are repeated violations punished?', 10, 12) %>%
    group_rows('How often will the agreement be renegotiated?', 13, 17) %>%
    group_rows('What punishments do they use?', 18, 21) %>%
    group_rows('Who makes the rules?', 22, 26))
}
```

@@

```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
aux <- cj %>%
  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
  unique()

# Country
tab <- data.frame(table(aux$countryOrigin))
names(tab) <- c('Country', 'Frequency')
p<-ggplot(data=tab, aes(x = Country, y=Frequency)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=50, linetype="dashed", color = "black") + 
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$Country, y = tab$Frequency + 2)
p

# Elite type
tab <- data.frame(table(aux$groupOrigin))
names(tab) <- c('Group Origin', 'Frequency')
p<-ggplot(data=tab, aes(x = `Group Origin`, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$`Group Origin`, y = tab$Frequency + 5)
p
```

@@

# Who makes the rules
tab <- data.frame(table(aux$`Who makes the rules?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('Who makes the rules?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are conflicts resolved?
tab <- data.frame(table(aux$`How are conflicts resolved?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are conflicts resolved?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# What punishments do they use?
tab <- data.frame(table(aux$`What punishments do they use?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('What punishments do they use?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 40) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are repeated violations punished?
tab <- data.frame(table(aux$`How are repeated violations punished?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are repeated violations punished?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are costs distributed?
tab <- data.frame(table(aux$`How are costs distributed?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are costs distributed?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How often will the agreement be renegotiated?
tab <- data.frame(table(aux$`How often will the agreement be renegotiated?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How often will the agreement be renegotiated?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

@@

The code for Figure 2 of the paper follows below, with also the point estimates in a companion table.

@@

# Plot
mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0=0.5)
p <- plot(mms, vline = 0.5)
p
ggsave(filename = 'MM_all.pdf', plot = p, width = 6, height = 5)

# Table
table_mm(mms, capt = 'Marginal Means -- Full Dataset')
```

@@

```{r, fig.width = 10, fig.height = 10}
# Changing country labels
arg$country <- 'Argentina'
bol$country <- 'Bolivia'
bra$country <- 'Brazil'
chi$country <- 'Chile'
col$country <- 'Colombia'
cri$country <- 'Costa Rica'
ecu$country <- 'Ecuador'
mex$country <- 'Mexico'
pan$country <- 'Panama'
per$country <- 'Peru'
# Plot by country
p <- plot(rbind(arg, bol, bra, chi, col, 
              cri, ecu, mex, pan, per), 
        group = 'country', vline = 0.5, nr = 10) +
  facet_wrap( ~ country, ncol = 5)

@@

ggsave(filename = 'MM_country.pdf', 
       plot = p, width = 12, height = 12)
```

The code for Figure 4 of the paper follows below, with also the point estimates in a companion table.

@@

```{r, fig.width = 7, fig.height = 8}
# Changing labels
res1$MemberType <- 'Executive'
res2$MemberType <- 'Legislative'
res3$MemberType <- 'Civil Society'
res4$MemberType <- 'Academia'

# Plot by Elite Type
p <- plot(rbind(res1, res2, res3, res4), 
     group = 'MemberType', vline = 0.5, nr=4) + 
  facet_wrap( ~ MemberType, ncol=4)
p

ggsave(filename = 'MM_membertype.pdf', plot = p, 
       width = 8, height = 5)
```

@@

results <- 
  cjoint::amce(fm, data=cj, cluster=T, 
               respondent.id="Response.ID", 
               design=conjDesign, 
               baselines = baselines, na.ignore = T)

# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Full Model')
```

@@

```{r, fig.width = 7, fig.height = 8}
# Plot AMCE -- Full Model
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Full Model',
     attribute.names = attrs)
```

@@

## Argentina
results <- cjoint::amce(fm, data=cj, cluster=TRUE,
                        respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Argentina')
# AMCE -- Argentina Only
tableAMCE(results, capt = 'AMCE -- Argentina Only')
```

@@

```{r}
## Bolivia
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Bolivia')
# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Bolivia Only')
```

@@

```{r}
## Brazil
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Brazil')
# Table AMCE -- Brazil Only
tableAMCE(results, capt = 'AMCE -- Brazil Only')
```

@@

```{r}
## Chile
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Chile')
# Table AMCE -- Chile Only
tableAMCE(results, capt = 'AMCE -- Chile Only')
```

@@

```{r}
## Colombia
results <- cjoint::amce(fm, data=cj, cluster=TRUE, 
                        respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Colombia')
# Table AMCE -- Colombia Only
tableAMCE(results, capt = 'AMCE -- Colombia Only')
```

@@

```{r}
## Costa Rica
results <- cjoint::amce(fm, data=cj, cluster=TRUE,
                        respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Costa Rica')
# Table AMCE -- Costa Rica Only
tableAMCE(results, capt = 'AMCE -- Costa Rica Only')
```

@@

```{r}
## Ecuador
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Ecuador')
# Table AMCE -- Ecuador Only
tableAMCE(results, capt = 'AMCE -- Ecuador Only')
```

@@

```{r}
## Mexico
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Mexico')
# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Mexico Only')
```

@@

```{r}
## Panama
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Panama')
# Table AMCE -- Panama Only
tableAMCE(results, capt = 'AMCE -- Panama Only')
```

@@

```{r}
## Peru
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Peru')
# Table AMCE -- Peru Only
tableAMCE(results, capt = 'AMCE -- Peru Only')
```

@@

# Executive
results <- cjoint::amce(fm, data=cj, cluster=TRUE,
                        respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$groupOrigin=='Executive')
# Table AMCE -- Executive Only
tableAMCE(results, capt = 'AMCE -- Executive Only')
```

>>>>

---
title: |
       | Supplementary Materials for "Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries"
author: 
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "David Skarbek[^skarbek]"
date: July 25, 2019
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

```{r setup, echo=FALSE}

@@

@@

```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
load('freire-mignozzetti-skarbek.RData')

aux <- cj %>%
  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
  unique()

# Country
tab <- data.frame(table(aux$countryOrigin))
names(tab) <- c('Country', 'Frequency')
p<- ggplot(data = tab, aes(x = Country, y = Frequency)) +
  geom_bar(stat = "identity") +
  geom_hline(yintercept = 50, linetype = "dashed", color = "black") + 
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$Country, y = tab$Frequency + 2)
p

# Elite type
tab <- data.frame(table(aux$groupOrigin))
names(tab) <- c('Group Origin', 'Frequency')
p<- ggplot(data = tab, aes(x = `Group Origin`, y = Frequency)) +
  geom_bar(stat = "identity") +
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$`Group Origin`, y = tab$Frequency + 5)
p
```

@@

# Who makes the rules
tab <- data.frame(table(aux$`Who makes the rules?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('Who makes the rules?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are conflicts resolved?
tab <- data.frame(table(aux$`How are conflicts resolved?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are conflicts resolved?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# What punishments do they use?
tab <- data.frame(table(aux$`What punishments do they use?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('What punishments do they use?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 40) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are repeated violations punished?
tab <- data.frame(table(aux$`How are repeated violations punished?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are repeated violations punished?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are costs distributed?
tab <- data.frame(table(aux$`How are costs distributed?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are costs distributed?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How often will the agreement be renegotiated?
tab <- data.frame(table(aux$`How often will the agreement be renegotiated?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How often will the agreement be renegotiated?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

@@

The code for Figure 2 of the paper follows below. We also include the point estimates in companion tables.

@@

# Plot
mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0 = 0.5)

myFaces <- c(rep('plain', 5), "bold",
             rep('plain', 4), "bold",
             rep('plain', 3), "bold",
             rep('plain', 4), "bold",
             rep('plain', 5), "bold",
             rep('plain', 5), "bold")

p <- plot(mms, vline = 0.5, header_fmt = "%s", size = 2) +
  ggplot2::theme(
    legend.position = "none",
    panel.grid.major = ggplot2::element_blank(),
    panel.grid.minor = ggplot2::element_blank(),
    axis.text.y = element_text(face=myFaces, size = 11)) + 
    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
                                                xmax = "upper"),
                            size = 0.5, height = 0, na.rm = TRUE)
p

ggsave(filename = 'MM_all.pdf', plot = p, width = 6, height = 5)

# Table
table_mm <- function(mms, capt) {
  dfr <- data.frame(feature = mms[,c(4)], 
             round(mms[,c(5,6,8,9,10)], digits=3))
  names(dfr) <- c('Feature', 'Estimate', 'Std.Error',
                'P-Value', 'Lower', 'Upper')
  return(kable(dfr, "latex", caption = capt, booktabs = T) %>%
    kable_styling(font_size = 10) %>%
    group_rows('Who makes the rules?', 1, 5) %>%
    group_rows('How are conflicts resolved?', 6, 10) %>%
    group_rows('What punishments do they use?', 11, 14) %>%
    group_rows('How are repeated violations punished?', 15, 17) %>%
    group_rows('How are costs distributed?', 18, 21) %>%
    group_rows('How often will the agreement be renegotiated?', 22, 26))
}

table_mm(mms, capt = 'Marginal Means -- Full Dataset')
```

@@

```{r, fig.width = 13, fig.height = 13}
# Changing country labels
arg$country <- 'Argentina'
bol$country <- 'Bolivia'
bra$country <- 'Brazil'
chi$country <- 'Chile'
col$country <- 'Colombia'
cri$country <- 'Costa Rica'
ecu$country <- 'Ecuador'
mex$country <- 'Mexico'
pan$country <- 'Panama'
per$country <- 'Peru'
# Plot by country
p <- plot(rbind(arg, bol, bra, chi, col, 
              cri, ecu, mex, pan, per), 
        group = 'country', vline = 0.5, nr = 10,
        header_fmt = "%s", size = 2) +
  facet_wrap( ~ country, ncol = 5) +
  ggplot2::theme(
    axis.text.y = element_text(face=myFaces, size = 13)) + 
    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
                                                xmax = "upper"),
                            size = 0.75, height = 0, na.rm = TRUE)

@@

ggsave(filename = 'MM_country.pdf', 
       plot = p, width = 10, height = 12)
```

The code for Figure 4 of the paper is available below. Tables displaying the point estimates are also included.

@@

```{r, fig.width = 10, fig.height = 8}
# Changing labels
res1$MemberType <- 'Executive'
res2$MemberType <- 'Legislative'
res3$MemberType <- 'Civil Society'
res4$MemberType <- 'Academia'

# Plot by Elite Type
p <- plot(rbind(res1, res2, res3, res4), 
     group = 'MemberType', vline = 0.5, nr = 4,
        header_fmt = "%s", size = 2) + 
  facet_wrap( ~ MemberType, ncol = 4) +
  ggplot2::theme(
    axis.text.y = element_text(face=myFaces, size = 11)) + 
    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
                                                xmax = "upper"),
                            size = 0.5, height = 0, na.rm = TRUE,
                            position = ggstance::position_dodgev(height = 1))
p

ggsave(filename = 'MM_membertype.pdf', plot = p,
       width = 8, height = 6)
```

@@

results <- cjoint::amce(fm, data = cj, cluster = TRUE, 
                        respondent.id = "Response.ID", 
                        design = conjDesign, 
                        baselines = baselines, na.ignore = T)

# Table AMCE -- Full Model 
tableAMCE <- function(results, capt = 'Main Model') {
  aux <- plotAMCE(results, ci = 0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Full Model',
     attribute.names = attrs, tblfy = T)
  aux <- aux %>%
    filter(!is.na(group)) %>%
    select(printvar, pe, se, lower, upper)
  indx <- grep('Baseline =', aux$printvar)
  aux$pe <- round(aux$pe, digits = 3)
  aux$se <- round(aux$se, digits = 3)
  aux$lower <- round(aux$lower, digits = 3)
  aux$upper <- round(aux$upper, digits = 3)
  aux$pe[indx] = ''
  aux$se[indx] = ''
  aux$lower[indx] = ''
  aux$upper[indx] = ''
  names(aux) <- c('Feature', 'Estimate', 'Std.Error', 
                  'Lower', 'Upper')
  return(kable(aux, "latex", caption = capt, booktabs = T, align = c('l', rep('c', 4))) %>%
    kable_styling(font_size = 10) %>%
    group_rows('How are conflicts resolved?', 1, 5) %>%
    group_rows('How are costs distributed?', 6, 9) %>%
    group_rows('How are repeated violations punished?', 10, 12) %>%
    group_rows('How often will the agreement be renegotiated?', 13, 17) %>%
    group_rows('What punishments do they use?', 18, 21) %>%
    group_rows('Who makes the rules?', 22, 26))
}

tableAMCE(results, capt = 'AMCE -- Full Model')
```

@@

```{r, fig.width = 7, fig.height = 8}
# Plot AMCE -- Full Model
plot(results, ci = 0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Full Model',
     attribute.names = attrs)
```

@@

## Argentina
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Argentina')
# AMCE -- Argentina Only
tableAMCE(results, capt = 'AMCE -- Argentina Only')
```

@@

```{r}
## Bolivia
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Bolivia')
# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Bolivia Only')
```

@@

```{r}
## Brazil
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Brazil')
# Table AMCE -- Brazil Only
tableAMCE(results, capt = 'AMCE -- Brazil Only')
```

@@

```{r}
## Chile
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Chile')
# Table AMCE -- Chile Only
tableAMCE(results, capt = 'AMCE -- Chile Only')
```

@@

```{r}
## Colombia
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Colombia')
# Table AMCE -- Colombia Only
tableAMCE(results, capt = 'AMCE -- Colombia Only')
```

@@

```{r}
## Costa Rica
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Costa Rica')
# Table AMCE -- Costa Rica Only
tableAMCE(results, capt = 'AMCE -- Costa Rica Only')
```

@@

```{r}
## Ecuador
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Ecuador')
# Table AMCE -- Ecuador Only
tableAMCE(results, capt = 'AMCE -- Ecuador Only')
```

@@

```{r}
## Mexico
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Mexico')
# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Mexico Only')
```

@@

```{r}
## Panama
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Panama')
# Table AMCE -- Panama Only
tableAMCE(results, capt = 'AMCE -- Panama Only')
```

@@

```{r}
## Peru
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$countryOrigin == 'Peru')
# Table AMCE -- Peru Only
tableAMCE(results, capt = 'AMCE -- Peru Only')
```

@@

# Executive
results <- cjoint::amce(fm, data = cj, cluster = TRUE,
                        respondent.id = "Response.ID", 
                        design = conjDesign, baselines = baselines,
                        subset = cj$groupOrigin == 'Executive')
# Table AMCE -- Executive Only
tableAMCE(results, capt = 'AMCE -- Executive Only')
```
